`SCPCL000824` - Exploration of gene set based methods for tumor cell assignment

### 2024-07-02 analyses/cell-type-ewings/exploratory_analysis/annotation_notebooks/SCPCS000492/SCPCL000824_tumor-gene-expression-exploration.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

Now we will look at the gene set scores for each gene set in `SCPCL000822` and `SCPCL000824`.  
The gene set scores correspond to the mean expression of all genes in a given gene set for a single cell with no scaling. 
The normalized gene expression was used as input to calculating the mean.

@@

One caveat is that `AUCell` relies on having a bimodal distribution in gene set expression, so I expect we may need to do a similar thing where we use cutoffs determined in `SCPCL000822` to call cells in `SCPCL000824`.

@@

# assign cells based on threshold and output plots 
ref_assignment <- AUCell::AUCell_exploreThresholds(ref_auc, assign = TRUE)
```

@@

Let's use the threshold identified by `AUCell` for `SCPCL000822` to identify tumor cells in `SCPCL000824`.  
Here, we label any cells that have passed the threshold set for the marker gene sets as tumor cells.

@@

It looks like we get pretty good agreement between using `UCell` with the `RIGGI` gene set to the original classification. 
Now we will use the cutoff from `SCPCL000822` to classify tumor cells in `SCPCL000824`.

>>>>

Now we will look at the gene set scores for each gene set in `SCPCL000822` and `SCPCL000824`.  
The gene set scores for each cell are the mean normalized expression of all genes in a given gene set with no scaling.

@@

One caveat is that `AUCell` relies on having a bimodal distribution in gene set expression to find a threshold, so I expect we may need to do a similar thing where we use thresholds determined in `SCPCL000822` to call cells in `SCPCL000824`.

@@

# assign cells for each gene set based on thresholds and output plots 
ref_assignments <- AUCell::AUCell_exploreThresholds(ref_auc, assign = TRUE)
```

@@

Let's use the marker gene threshold identified by `AUCell` for `SCPCL000822` to identify tumor cells in `SCPCL000824`.  
Here, we label any cells that have passed the threshold set for the marker gene set as tumor cells.

@@

It looks like we get pretty good agreement between using `UCell` with the `RIGGI` gene set to the original classification. 
Now we will use the marker gene set cutoff from `SCPCL000822` to classify tumor cells in `SCPCL000824`.
